A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex
a

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefit from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. We also present a
 pseudo energy model taking into account the energetic contribution 
of the stacked base pairs and the isostericity of all base pairs.

>>>>

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefit from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. We also develop a new
 pseudo energy model, taking into account the nearest-neighbour energy model 
and the isostericity,  quantifying geometrical differences, of all base pairs.
